IN FOCUS \\ Natural history matters: how biological constraints shape diversified interactions in pollination networks

### 2016-07-07 ms_infocus.tex
Reordered refs.
Minor edits.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MS: In Focus comment paper for Journal of Animal Ecology.
%% Draft
%% April 2016
%% Revised version: 
%% Original version wordcount: 1718 words.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,12pt]{article}
\usepackage{comment}
\usepackage{jae}
\title{IN FOCUS \\ Natural history matters: how biological constraints shape diversified interactions in pollination networks}
\running{Forbidden interactions}

@@

\nwords{1718}
\ntables{0}
\nfig{2}
\nref{14}

@@

 Phenotypic fitting of corolla length and shape and the pollinators' feeding apparatus and body sizes are important because the better the fit, the better the consequences in terms of fitness outcomes for the interaction partners \citep{Nilsson:1988}. Yet the expectation of perfect trait matching across populations or communities is too simplistic \citep{Anderson:2010}: "arms races" as initially suggested by Darwin and Wallace are frequently asymmetric, originating pollinator shifts rather than tight phenotypic trait matching (Fig. 2). Extensive local variation in phenotypic mismatch exists in different plant-pollinator systems \citep[e.g., ][]{Cocucci:2009,Anderson:2010,More:2012}, with pollinator-mediated selection geographic mosaics of locally coevolved partners.

@@

@@

\bibitem{More:2012}
Moré, M., Amorim, F.W., Benitez-Vieyra, S., Medina, A.M., Sazima, M. \& Cocucci, A.A. (2012) Armament imbalances: match and mismatch in plant-pollinator traits of highly specialized long-spurred orchids (ed M. Heil). PLoS ONE, 7, e41878.

@@

\begin{figure}[h!]
  \caption{Morphological mismatches set important biological constraints for size-limited foragers, including e.g., predators, pollinators, and frugivores. In plant-animal mutualisms (e.g., plant-pollinator interactions), a morphological mismatch between partners sets size limits that filter out a range of phenotypes that otherwise could eventually interact. Other reasons for forbidden links include, e.g., phenological differences \citep{BasJor:2014}. Thus, a number of the potential interactions that could take place in a given mutualistic assemblage simply cannot occur because of biological reasons: these are forbidden interactions. Photo: Andrea Cocucci. An sphingid moth, \textit{Agrius cingulata}, visiting a flower of \textit{Bauhinia mollis} (Fabaceae), Las Yungas, Argentina.}
  \label{Fig1}
  \begin{center}
    \includegraphics[width=14cm]{Fig1}
  \end{center}
\end{figure}

\begin{figure}[h!]
  \caption{The mechanistic basis of morphological mismatches in hawkmoth-flower interactions. Two main coevolutionary trends in hawkmoth-flower interactions involve arms-race trends (with progressively longer spurs and proboscides) and pollinator shifts (where short-tongued moths are replaced as legitimate pollinators by long-tongued species when corolla tubes increase in length). Pollination is impossible when the proboscis is longer than the spurs because the pollen or pollinaria are attached further from the base of the proboscis. When this happens the pollinaria are scratched away by the forelegs when the proboscis is rolled to a loose spiral. If the proboscis is shorter than the spur, transfer of the pollinaria is possible as long as the proboscis can get in contact with the sexual organs of the orchid. For example, nectar accessibility in \textit{Angraecum sesquipedale} long-tubed flowers. A,  only small volumes of nectar can be exploited if the spur is 27 cm long. B, moths with an average tongue length of 22 cm can obtain about 50 $\mu L$ nectar from a spur of 33.3 cm average length and an average nectar volume of 165 $\mu L$. C, a spur 43 cm long could offer nectar to a moth with a 22-cm-long proboscis only if it contains more than 240 $\mu L$ nectar. Lack of fit prevents interactions, but also marginal fitting renders interactions unlikely because of energetic constraints. Modified and redrawn from \citep{Arditti:2012}.}
  \label{Fig2}
  \begin{center}
    \includegraphics[width=10cm]{Fig2}
  \end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% MS NOTES
\begin{comment}
Arditti et al. Fig 11 legend:
Figure 11. Nectar: sugar content and height of column, proboscis length and coevolution. A, correlation between spur length and extracted nectar volume (modified from Wasserthal, 1997 by the removal of data about species other than Angraecum sesquipedale and the addition of the five lines of text at the base of the figure). B, correlation between height of nectar column and nectar volume measured by extraction and injection (modified from Wasserthal, 1997 by the addition of the two lines of text which start with ‘Mean’). C, comparison between Darwin’s ‘coevolution race’ and Wasserthal’s ‘pollinator shift’ models. In the ‘coevolution race’ model (A) the race is between increasing lengths of spurs and proboscises. The ‘pollination shift’ model (B) involves the recruitment by long-spurred angraecoid orchids of pollinators which are generalist feeders and have proboscises of different lengths. These pollinators are substituted gradually. When spurs enlarge beyond a certain length due to evolutionary pressure by the primary visitors flowers can be exploited (i.e. nectar can be taken from them) by illegitimate visitors with longer proboscises (*). This has been observed in interactions between Xanthopan morganii praedicta and Coelonia solani with Angraecum compactum. Increased selective pressure is exerted by the existence of moth species with long proboscises. Flowers become deceptive, but can still be pollinated when spurs become too long for the primary pollinator to reach the nectar. Pollination is impossible when the proboscis is longer than the spurs because the pollinaria are attached further from the base of the proboscis. When this happens the pollinaria are scratched away by the forelegs when the proboscis is rolled to a loose spiral. If the proboscis is shorter than the spur, transfer of the pollinaria is possible as long as the proboscis can get in contact with the sexual organs of the orchid. This occurs in other angrecoid orchids. Explanation of symbols: *, illegitimate visitor with a long proboscis which exploits flowers; black moth, orchid pollinator; grey moth, non-pollinating visitor; white moth, a moth incapable of pollinating an orchid (modified from Wasserthal, 1997 by moving and adding labels). D, correlation between position of fully inserted proboscis and time of insertion, stay and withdrawal (modified from Wasserthal, 1997 by the removal of data not pertaining to Angraecum sesquipedale). E, Nectar accessibility in Angraecum sesquipedale spurs. a, moth with an average spur length of 22 cm can obtain about 50 mL nectar from a spur of average length of 33.3 cm and an average nectar volume of 165 ml. b, a spur 43 cm long could offer nectar to a moth with a 22-cm-long proboscis only if it contains more than 240 mL solution. C, small volumes of nectar can be exploited if the spur is 27 cm long (Wasserthal, 1997).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MS: In Focus comment paper for Journal of Animal Ecology.
%% Draft
%% April 2016
%% Revised version: 
%% Original version wordcount: 1716 words.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,12pt]{article}
\usepackage{comment}
\usepackage{jae}
\title{IN FOCUS \\ Natural history matters: how biological constraints shape diversified interactions in pollination networks}
\running{Forbidden interactions}

@@

\nwords{1716}
\ntables{0}
\nfig{2}
\nref{14}

@@

 Phenotypic fitting of corolla length and shape and the pollinators' feeding apparatus and body sizes are important because the better the fit, the better the consequences in terms of fitness outcomes for the interaction partners \citep{Nilsson:1988}. Yet the expectation of perfect trait matching across populations or communities is too simplistic \citep{Anderson:2010}: "arms races" as initially suggested by Darwin and Wallace are frequently asymmetric, originating pollinator shifts rather than tight phenotypic trait matching (Fig. 2)\citep{Wasserthal:2014}. Extensive local variation in phenotypic mismatch exists in different plant-pollinator systems \citep[e.g., ][]{Cocucci:2009,Anderson:2010,More:2012}, with pollinator-mediated selection geographic mosaics of locally coevolved partners.

@@

\bibitem{More:2012}
Moré, M., Amorim, F.W., Benitez-Vieyra, S., Medina, A.M., Sazima, M. \& Cocucci, A.A. (2012) Armament imbalances: match and mismatch in plant-pollinator traits of highly specialized long-spurred orchids. PLoS ONE, 7, e41878.

@@

@@

\begin{figure}[h!]
  \caption{Morphological mismatches set important biological constraints for size-limited foragers, including e.g., predators, pollinators, and frugivores. In plant-animal mutualisms (e.g., plant-pollinator interactions), a morphological mismatch between partners sets size limits that filter out a range of phenotypes that otherwise could eventually interact. Two main coevolutionary trends in hawkmoth-flower interactions involve arms-race trends (with progressively longer spurs and proboscides) and pollinator shifts (where short-tongued moths are replaced as legitimate pollinators by long-tongued species when corolla tubes increase in length). Pollination is impossible when the proboscis is longer than the spurs because the pollen or pollinaria are attached further from the base of the proboscis. When this happens the pollen or pollinaria are scratched away by the forelegs when the proboscis is rolled to a loose spiral. If the proboscis is shorter than the spur, transfer of the pollen or pollinaria is possible as long as the proboscis can get in contact with the sexual organs of the orchid. Other reasons for forbidden links include, e.g., phenological differences \citep{BasJor:2014}. Thus, a number of the potential interactions that could take place in a given mutualistic assemblage simply cannot occur because of biological reasons: these are forbidden interactions. Photo: courtesy of Andrea Cocucci. A sphingid moth, \textit{Agrius cingulata}, visiting a flower of \textit{Bauhinia mollis} (Fabaceae), Las Yungas, Argentina.}
  \label{Fig1}
  \begin{center}
    \includegraphics[width=12cm]{Fig1}
  \end{center}
\end{figure}

\begin{figure}[h!]
  \caption{The mechanistic basis of morphological mismatches in hawkmoth-flower interactions. For example, nectar accessibility in \textit{Angraecum sesquipedale} long-tubed flowers. A,  only small volumes of nectar can be exploited if the spur is 27 cm long. B, moths with an average tongue length of 22 cm can obtain about 50 $\mu L$ nectar from a spur of 33.3 cm average length and an average nectar volume of 165 $\mu L$. C, a spur 43 cm long could offer nectar to a moth with a 22-cm-long proboscis only if it contains more than 240 $\mu L$ nectar. Lack of fit prevents interactions, but also marginal fitting renders interactions unlikely because of energetic constraints. Modified and redrawn from \citep{Arditti:2012}.}
  \label{Fig2}
  \begin{center}
    \includegraphics[width=13cm]{Fig2}
  \end{center}
\end{figure}
%---------------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% MS NOTES
\begin{comment}
Arditti et al. Fig 11 legend:
Figure 11. Nectar: sugar content and height of column, proboscis length and coevolution. A, correlation between spur length and extracted nectar volume (modified from Wasserthal, 1997 by the removal of data about species other than Angraecum sesquipedale and the addition of the five lines of text at the base of the figure). B, correlation between height of nectar column and nectar volume measured by extraction and injection (modified from Wasserthal, 1997 by the addition of the two lines of text which start with ‘Mean’). C, comparison between Darwin’s ‘coevolution race’ and Wasserthal’s ‘pollinator shift’ models. In the ‘coevolution race’ model (A) the race is between increasing lengths of spurs and proboscises. The ‘pollination shift’ model (B) involves the recruitment by long-spurred angraecoid orchids of pollinators which are generalist feeders and have proboscises of different lengths. These pollinators are substituted gradually. When spurs enlarge beyond a certain length due to evolutionary pressure by the primary visitors flowers can be exploited (i.e. nectar can be taken from them) by illegitimate visitors with longer proboscises (*). This has been observed in interactions between Xanthopan morganii praedicta and Coelonia solani with Angraecum compactum. Increased selective pressure is exerted by the existence of moth species with long proboscises. Flowers become deceptive, but can still be pollinated when spurs become too long for the primary pollinator to reach the nectar. Pollination is impossible when the proboscis is longer than the spurs because the pollinaria are attached further from the base of the proboscis. When this happens the pollinaria are scratched away by the forelegs when the proboscis is rolled to a loose spiral. If the proboscis is shorter than the spur, transfer of the pollinaria is possible as long as the proboscis can get in contact with the sexual organs of the orchid. This occurs in other angrecoid orchids. Explanation of symbols: *, illegitimate visitor with a long proboscis which exploits flowers; black moth, orchid pollinator; grey moth, non-pollinating visitor; white moth, a moth incapable of pollinating an orchid (modified from Wasserthal, 1997 by moving and adding labels). D, correlation between position of fully inserted proboscis and time of insertion, stay and withdrawal (modified from Wasserthal, 1997 by the removal of data not pertaining to Angraecum sesquipedale). E, Nectar accessibility in Angraecum sesquipedale spurs. a, moth with an average spur length of 22 cm can obtain about 50 mL nectar from a spur of average length of 33.3 cm and an average nectar volume of 165 ml. b, a spur 43 cm long could offer nectar to a moth with a 22-cm-long proboscis only if it contains more than 240 mL solution. C, small volumes of nectar can be exploited if the spur is 27 cm long (Wasserthal, 1997).
